Combining information from photometric and spectroscopic data:\\ Probabilistic spectrophotometric inference

### 2015-06-16 tex/ms.tex
prettify noise_realization figure, some minor changes in discussion text

\begin{document}\sloppy\sloppypar
\title{Combining information from photometric and spectroscopic data:\\
  Probabilistic spectrophotometric inference}
\shorttitle{Combining Spectroscopy and Photometry}
\author{
  BDJ\altaffilmark{\lick},
  DRW\altaffilmark{\lick},
  DFM\altaffilmark{\ccpp},
  DWH\altaffilmark{\ccpp, \cds, \mpia},
  CC\altaffilmark{\lick},
  others}
\shortauthors{bdj et al}
\altaffiltext{\lick}{University of California Lick Observatory}
\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{\cds}{Center for Data Science, New York University}
\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie}

@@

\subsection{Real Data: \excluster} 
We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, \excluster, using the full YY-band
photometry. In Figure \ref{fig:inferred_spectrum} we show the spectra
that result from draws of the parameters $[\theta,\alpha]$ from the
posterior distribution, as well as several of the individual
components of the model constructed from each draw. Figure
\ref{fig:inferred_spectrum} also shows the calibrated spectrum on
which the priors were conditioned, and residuals between the posterior
models and the observed data.

In Figure \ref{fig:inferred_sed} we show the corresponding SED for the
posterior parameter draws, compared to the observed SED. There is some
tension between the modeled and observed SEDs, I'm not quite sure
why. Finally, In Figure \ref{fig:inferred_params} we show the
marginalized and joint PDFs for a subset of the full model parameters.

It is possible to reconstruct the inferred total multiplicative
calibration vector for each draw of the model parameters (Equation
\ref{eq:calibration}) If the spectrophotometric calibration were
perfect and we had correctly inferred it, then we would expect this
vector to be constant as a function of wavelength.

@@

We have demonstrated, using using both mock and real spectra of
galactic stellar clusters, that we can combine photometric and
spectroscopic data in a principled way to infer physical properties.
We do not resort to an arbitrary down-weighting or up-weighting of
certain data. Instead, we explicitly and flexibly model our uncertain
knowledge of the spectral calibration and infer this calibration
jointly with the physical properties. For a number of applications
this combination of spectroscopy and photometry reduces the need for
spectrophotometric calibration entirely, such that the less expensive
photometric calibration is sufficient.  Additional calibration
information, if it exists, can be incorporated into informative priors
on the calibration parameters of the model, inform the construction of
the calibration model (including the form of the covariance kernel),
or approximately remove gross features that are difficult to model
parametrically or via a Gaussian Process.  {\color{blue} Discuss more
complicated covariance kernels, multiple kernels.}

@@

Our strategy is easily extensible to more complicated models, which
include for example night sky-line emission in the spectroscopy
\citep[e.g.,][]{gullikson14} or residuals from an intial sky-line
subtraction and uncertainties in wavelength calibration
\citep[e.g.,][]{walker15}. Furthermore, more complex physical models
may be considered for the mean object model, for example including SFH
parameters so as to model galaxies. {\color{blue} Discuss background
modeling}

In a heirarchical modelling context it should be possible to use the
inferred calibration parameters, along with additional information
about the observations (e.g. airmass, instrument temperature), to in
turn infer the parameters of a generative model for the calibration
\citep[e.g.][]{spectrophot}. This generative model can then be used in
the (probabilistic) calibration of objects where the spectra are
difficult to model explicitly.

Limitations.  The strategy we have advocated has several limitations.
First, it requires a generative model for the spectrum of the object
of interest, and is thus ill-suited to discovery projects.  Second,
care must be taken to avoid absorbing interesting model deficiencies
into the calibration model. For example, in the model we have
described, it is possible that broad shallow features (for example due
to molecular bands or absorption line complexes) will be absorbed into
the Gaussian process if not properly included in the mean
model. Third, we have made the assumption that the spectroscopy and
the photometry are sampling the same populations.  In practice,
differences between spectroscopic and photometric apertures often mean
that the photometry and the spectroscopy are sampling slightly
different physical regions.  The correct response to this situation is
to explicitly model the differences, incorporating prior information
about the spatial variation of physical properties.  Fourth, the
method will break down at very low S/N due to the logarithmic
formulation of the residual in equation~(\ref{eq:spectroscopicLF}).
Finally, this method is computationally intensive and expensive, since
we are constantly inverting largish matrices.

{\color{blue} BDJ - This paragraph is probably too calibration
focused. We want to focus more on spec + phot combinations.  At least,
this paragraph should not be in the discussion section.}
Fundamentally, calibration involves observing a `known' or `truth'
with an instrument, and using that observation to infer the effects of
the instrument.  However, we do not have knowledge of a single truth
for any object, only relative probabilities for what might be true.
In this sense, one should never use a single point estimate of the
spectrophotometric calibration, the full distribution of the possible
calibrations should be inferred from our probabilistic knowledge of
the calibration object and forward propogated
\citep[e.g.][]{lee11}. Indeed, even if the calibration object is known
perfectly, the observation of it will be noisy and thus so will the
inferred calibration. Once this forward propogation of calibration
uncertainty is done, the only distinction between 'calibration'
objects and targets of interest is the uncertainty in the model for
the object and the level of uncertainty in the observed object
spectrum -- this is why calibration objects are typically bright and
simple.  If one is interested in inferring parameters of interest of
spectral models of astrophysical objects, then there is often no
reason not to use those objects themselves as calibration objects,
especially if you expect your calibration to be spatially or 
temporally variable, or to change with the brightness of the object.

@@

\acknowledgements
Thanks to X. for bringing us beer.
DRW is supported by NASA through Hubble Fellowship grant
  HST-HF-51331.01 awarded by the Space Telescope Science Institute.
BDJ and DRW acknowledge the hospitality of Hans-Walter Rix and the MPIA. 
CC is supported by Packard and Sloan Foundation Fellowships. 
This research made extensive use of NASA's Astrophysics Data System Bibliographic Services. 
In large part, analysis and plots presented in this paper utilized
  iPython and packages from NumPy, SciPy, and Matplotlib
  \citep[][]{hunter2007, oliphant2007, perez2007} as well
  as python-FSPS  (\url{http:://github.com/dfm/python-fsps}) .

>>>>

\begin{document}\sloppy\sloppypar
\title{Combining information from photometric and spectroscopic data:\\
  Probabilistic spectrophotometric inference}
\shorttitle{Combining Spectroscopy and Photometry}
\author{
%  BDJ\altaffilmark{\lick},
%  DRW\altaffilmark{\lick},
%  DFM\altaffilmark{\ccpp},
%  DWH\altaffilmark{\ccpp, \cds, \mpia},
%  CC\altaffilmark{\lick},
  AUTHORS}
\shortauthors{BDJ et al}
%\altaffiltext{\lick}{University of California Lick Observatory}
%\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics, Department of Physics, New York University}
%\altaffiltext{\cds}{Center for Data Science, New York University}
%\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie}

@@

\subsection{Real Data: \excluster} 
We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, \excluster, using the $griz$-band
photometry. In Figure \ref{fig:real_calibrated} we show the spectra
that result from draws of the parameters $[\theta,\alpha]$ from the
posterior distribution, as well as several of the individual
components of the model constructed from each draw. Figure
\ref{fig:real_calibrated} also shows the marginalized PDFs for a
subset of the full model parameters.

It is possible to reconstruct the inferred total multiplicative
calibration vector for each draw of the model parameters (Equation
\ref{eq:calibration}). If the spectrophotometric calibration were
perfect and we had correctly inferred it, then we would expect this
vector to be constant as a function of wavelength.

@@

We have demonstrated, using using both mock and real spectra of
galactic stellar clusters, that we can combine photometric and
spectroscopic data in a principled way to infer physical properties.
We do not resort to an arbitrary down-weighting or up-weighting of
certain data. Instead, we explicitly and flexibly model our uncertain
knowledge of the spectral calibration and infer this calibration
jointly with the physical properties. For a number of applications
this combination of spectroscopy and photometry reduces the need for
spectrophotometric calibration entirely, such that the less expensive
photometric calibration is sufficient.  Additional calibration
information, if it exists, can be incorporated into informative priors
on the calibration parameters of the model, inform the construction of
the calibration model (including the form of the covariance kernel),
or approximately remove gross features that are difficult to model
parametrically or via a Gaussian Process.  {\color{blue} Discuss more
complicated covariance kernels, multiple kernels, combining fractional
and absolute covariance amplitudes.}

@@

Our strategy is easily extensible to more complicated models, which
include for example night sky-line emission in the spectroscopy
\citep[e.g.,][]{gullikson14} or residuals from an initial sky-line
subtraction and uncertainties in wavelength calibration
\citep[e.g.,][]{walker15}. Furthermore, more complex physical models
may be considered for the mean object model, for example including SFH
parameters so as to model galaxies. {\color{blue} Discuss background
modeling}

In a heirarchical modelling context it should be possible to use the
inferred calibration parameters, along with additional information
about the observations (e.g. airmass, instrument temperature), to in
turn infer the parameters of a generative model for the calibration
parameters \citep[e.g.][]{spectrophot}. This generative model can then
be used in the (probabilistic) calibration of objects where the
spectra are difficult to model explicitly.  One aspect of such
modelling might entail inferring the priors on the Gaussian Process
parameters $a$ and $\ell$.

Limitations.  The strategy we have advocated has several limitations.
First, it requires a generative model for the spectrum of the object
of interest, and is thus ill-suited to discovery projects.  Second,
care must be taken to avoid absorbing interesting model deficiencies
into the calibration model. For example, in the model we have
described, it is possible that broad shallow features (for example due
to molecular bands or absorption line complexes) will be absorbed into
the Gaussian process if not properly included in the mean
model. Third, we have made the assumption that the spectroscopy and
the photometry are sampling the same populations.  In practice,
differences between spectroscopic and photometric apertures often mean
that the photometry and the spectroscopy are sampling slightly
different physical regions.  The correct response to this situation is
to explicitly model the differences, incorporating prior information
about the spatial variation of physical properties.  Finally, this
method is computationally intensive and expensive, since we are
constantly inverting largish matrices.

{\color{blue} BDJ - This paragraph is probably too calibration
focused. We want to focus more on spec + phot combinations.  At least,
this paragraph should not be in the discussion section.}
Fundamentally, calibration involves observing a `known' or `truth'
with an instrument, and using that observation to infer the effects of
the instrument.  However, we do not have knowledge of a single truth
for any object, only relative probabilities for what might be true.
In this sense, one should never use a single point estimate of the
spectrophotometric calibration, the full distribution of the possible
calibrations should be inferred from our probabilistic knowledge of
the calibration object and forward propogated
\citep[e.g.][]{lee11}. Indeed, even if the calibration object is known
perfectly, the observation of it will be noisy and thus so will the
inferred calibration. Once this forward propogation of calibration
uncertainty is done, the only distinction between 'calibration'
objects and targets of interest is the uncertainty in the model for
the object and the level of uncertainty in the observed object
spectrum -- this is why calibration objects are typically bright and
simple.  If one is interested in inferring parameters of interest of
spectral models of astrophysical objects, then there is often no
reason not to use those objects themselves as calibrators,
especially if you expect your calibration to be spatially or 
temporally variable, or to change with the brightness or other
properties of the object.

@@

\acknowledgements
%Thanks to X. for bringing us beer.
%DRW is supported by NASA through Hubble Fellowship grant
%  HST-HF-51331.01 awarded by the Space Telescope Science Institute.
%BDJ and DRW acknowledge the hospitality of Hans-Walter Rix and the MPIA. 
%CC is supported by Packard and Sloan Foundation Fellowships. 
This research made extensive use of NASA's Astrophysics Data System Bibliographic Services. 
In large part, analysis and plots presented in this paper utilized
  iPython and packages from NumPy, SciPy, and Matplotlib
  \citep[][]{hunter2007, oliphant2007, perez2007} as well
  as python-FSPS  (\url{http:://github.com/dfm/python-fsps}) .
